Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-30 papers/ms.tex
update ms

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$
respectively \citep{chubak_2012}.  To infer the equivalent width of
the \ion{Li}{1} 6708\,\AA\ doublet, we followed the procedure
described by \citet{bouma_2021_ngc2516}.  This yielded a strong
detection: ${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with values
consistent at $<$$1$-$\sigma$ between the two epochs.   The quoted
value does not correct for the \ion{Fe}{1} blend at 6707.44\,\AA,
because HIRES resolves the two features.  Given the purported age and
effective temperature of the star, the lithium equivalent width is
somewhat low.  We discuss this in greater depth in
Appendix~\ref{app:spectra}.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.85\textwidth]{f3e.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3a.pdf}
			\includegraphics[width=0.33\textwidth]{f3b.pdf}
		}

		\vspace{-1.27cm}	
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3c.pdf}
			\includegraphics[width=0.33\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Raw and processed light curves for the Kepler Objects of
    Interest in Cep-Her.}   
    {\it Top}: 50 day light curve segment from the 3.9 years of Kepler
    data.  The ordinate shows the \texttt{PDCSAP} median-subtracted
    flux in units of parts-per-thousand ($\times 10^{-3}$).  The
    dominant signal is from starspots; planetary transit times
    are indicated but the individual transits are not visible at this scale.
    {\it Bottom}:
    Phase-folded transits of Kepler-1643, KOI-7913, KOI-7368, and
    Kepler-1627 with stellar variability removed.  The maximum a
    posteriori model is shown with the gray line, and the
    residual after subtracting the transit model is vertically
    displaced.  Windows over 10 hours are shown.  Gray points are
    individual flux measurements; black points are binned to 20 minute
    intervals, and have a representative 1-$\sigma$ error bar in the
    center-right of each panel. 
		\label{fig:planets}
	}
\end{figure*}

@@

It bears mentioning that KOI-7368 shows a weak centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
significant ($0\farcs2$; 3.0-$\sigma$).  Again, the data
validation reports show that the shift is caused by a few outlying
quarters (4, 5, 8, and 12).  The fact that the remaining data show a
consistent scatter between centroid locations suggests that these
outliers are also caused by the stellar variability.  
Our NIRC2 imaging independently shows that there are no neighboring
sources that could cause an offset of the observed amplitude.

\paragraph{KOI-7913}
KOI-7913.01 is also currently listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The \citet{morton_false_2016}
analysis was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01
to KOI-7620.01 (omitting KOI-7913.01).  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discussed ($\approx$$14$), its lower FPP relative to
KOI-7368 can be understood through its flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet is statistically validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate'' (see Appendix~\ref{app:koi7913}).  The most likely
explanation is the presence of KOI-7913~B, which is located
approximately one Kepler pixel away from Kepler-7913 A.  Our
pixel-level analysis of the target pixel files did not show any
evidence to support the idea that KOI-7913~B could host the transiting
planet.  Our NIRC2 imaging similarly ruled out the possibility of any
other plausible host star for the planet other than KOI-7913~A.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a
    factor of three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  Interesting trends in
    the population of planets younger than $10^8$ years old include {\it i)} their
    large sizes and {\it ii)} the lack of hot Jupiters.  The new
    objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

%\clearpage
\acknowledgements
\raggedbottom
% Cycle 3 and 4
L.G.B{.} acknowledges support from the Heising-Simons Foundation 51
Pegasi~b Fellowship and the TESS GI Program (NASA grants 80NSSC21K0335
and 80NSSC22K0298).
J.L.C{.} is supported by NSF AST-2009840 and the TESS GI Program (NASA
grant 80NSSC22K0299).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%%
%We thank the TESS architects
%%(G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, J.~Jenkins)
%and the many TESS team members for their
%efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
%Finally, this research has made use of the Keck Observatory Archive (KOA),
%which is operated by the W. M. Keck Observatory and the NASA Exoplanet
%Science Institute (NExScI), under contract with the National
%Aeronautics and Space Administration.
%We also thank the Keck Observatory staff for their support of
%HIRES and remote observing.  We recognize the importance that the
%summit of Maunakea has within the indigenous Hawaiian community, and
%are deeply grateful to have the opportunity to conduct observations
%from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

>>>>

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$
respectively \citep{chubak_2012}.  To infer the equivalent width of
the \ion{Li}{1} 6708\,\AA\ doublet, we followed the procedure
described by \citet{bouma_2021_ngc2516}.  This yielded a strong
detection: ${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with values
consistent at $<$$1$-$\sigma$ between the two epochs.   The quoted
value does not correct for the \ion{Fe}{1} blend at 6707.44\,\AA.  Given the purported age and
effective temperature of the star, the lithium equivalent width is
somewhat low.  We discuss this in greater depth in
Appendix~\ref{app:spectra}.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.85\textwidth]{f3a.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3b.pdf}
			\includegraphics[width=0.33\textwidth]{f3c.pdf}
		}

		\vspace{-1.27cm}	
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3d.pdf}
			\includegraphics[width=0.33\textwidth]{f3e.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Raw and processed light curves for the Kepler Objects of
    Interest in Cep-Her.}   
    {\it Top}: 50 day light curve segment from the 3.9 years of Kepler
    data.  The ordinate shows the \texttt{PDCSAP} median-subtracted
    flux in units of parts-per-thousand ($\times 10^{-3}$).  The
    dominant signal is from starspots; planetary transit times
    are indicated but the individual transits are not visible at this scale.
    {\it Bottom}:
    Phase-folded transits of Kepler-1643, KOI-7913, KOI-7368, and
    Kepler-1627 with stellar variability removed.  The maximum a
    posteriori model is shown with the gray line, and the
    residual after subtracting the transit model is vertically
    displaced.  Windows over 10 hours are shown.  Gray points are
    individual flux measurements; black points are binned to 20 minute
    intervals, and have a representative 1-$\sigma$ error bar in the
    center-right of each panel. 
		\label{fig:planets}
	}
\end{figure*}

@@

It bears mentioning that KOI-7368 shows a centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
significant ($0\farcs2$; 3.0-$\sigma$).  Again, the data
validation reports show that the shift is caused by a few outlying
quarters (4, 5, 8, and 12).  Since the remaining data show
consistent scatter in their centroid locations, these
outlying quarters are likely also caused by the stellar variability.  
Our NIRC2 imaging independently shows that there are no neighboring
sources that could cause an offset of the observed amplitude.

\paragraph{KOI-7913}
KOI-7913.01 is also currently listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The \citet{morton_false_2016}
analysis was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01
to KOI-7620.01 (omitting KOI-7913.01).  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
NIRC2 contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discussed ($\approx$$14$), its lower FPP relative to
KOI-7368 can be understood through its flat-bottomed shape,
combined with its long transit duration relative to most
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet is statistically validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate'' (see Appendix~\ref{app:koi7913}).  The most likely
explanation is the presence of KOI-7913~B, which is located
$\approx0.9$ Kepler pixels away from Kepler-7913 A.  
While the $\approx$1.5 pixel FWHM of the Kepler pixel response function
implies that there is blending between the two stars,
the target-pixel level data for KOI-7913 B reveals an
entirely different stellar rotation
period (Table~\ref{tab:sysparams}), and no hint of the transit signal.
This implies that KOI-7913 B cannot host the planet.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a
    factor of three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  Interesting trends in
    the population of planets younger than $10^8$ years old include {\it i)} their
    large sizes and {\it ii)} the lack of hot Jupiters.  The new
    objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

%\clearpage
\acknowledgements
\raggedbottom
% Cycle 3 and 4
L.G.B{.} is supported by the Heising-Simons Foundation 51
Pegasi~b Fellowship and the TESS GI Program (NASA grants 80NSSC21K0335
and 80NSSC22K0298).
R.K{.} is supported by the Heising-Simons Foundation.
J.L.C{.} is supported by NSF AST-2009840 and the TESS GI Program (NASA
grant 80NSSC22K0299).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%%
%We thank the TESS architects
%%(G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, J.~Jenkins)
%and the many TESS team members for their
%efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
%Finally, this research has made use of the Keck Observatory Archive (KOA),
%which is operated by the W. M. Keck Observatory and the NASA Exoplanet
%Science Institute (NExScI), under contract with the National
%Aeronautics and Space Administration.
%We also thank the Keck Observatory staff for their support of
%HIRES and remote observing.  We recognize the importance that the
%summit of Maunakea has within the indigenous Hawaiian community, and
%are deeply grateful to have the opportunity to conduct observations
%from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%
